Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme

### 2013-06-16 Report/article.tex
Check again

\begin{figure}[!h]
\centering
\includegraphics[width=7cm, height=6cm]{fsort3.pdf} 
\caption{Runtime for Insertion sort, nbit=4} 
\label{fig:image_sf3} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=7cm, height=6cm]{fsort4.pdf} 
\caption{Runtime for Insertion sort, nbit=6} 
\label{fig:image_sf4} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=7cm, height=6cm]{fsort5.pdf} 
\caption{Run time for Insertion sort, nbit=8} 
\label{fig:image_sf5} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!h]%on ouvre l'environnement figure
\centering
\includegraphics[width=7cm, height=6cm]{fsort6.pdf} 
\caption{CPU time for Insertion sort, nbit=4} 
\label{fig:image_sf6} %l'étiquette pour faire référence à cette image
\end{figure}

@@

\begin{figure}[!H]
\centering
\includegraphics[width=7cm, height=6cm]{fsort2.pdf} 
\caption{Runtime Comparison for insertion sort} 
\label{fig:image_sf2} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!H]%nouvre l'environnement figure
\centering
\includegraphics[width=7cm, height=6cm]{fsort1.pdf} 
\caption{Curve fitting for insertion sort}
\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
\end{figure}

@@

When we increase the security of the system by setting the parameters to  $(N = 256,\eta  = 16, \mu = 2, s_1 = 5000, s_2 = 5)$(as suggested in \cite{cryptoeprint:2009:571}) which ensures $25$ bits of security, the Odd-Even sorting algorithm on  $4$ sequences, each of $4$ bits takes hours. By lowering the security level to only $8$ bits using the parameters :$(N = 16, \eta = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which we believe is an implementation bug in the bootstrapping mechanism. Lowering the security even further to only $5$ bits using the parameters: $(N = 8, \eta = 2^8, \mu = 4, s_1 = 65, s_2 = 5)$, and testing odd-even sorting for $32$ sequences of $6$ bits each took more than an hour. However, increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \eta = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2}. The results show that this set of parameters provide a better security and at almost no extra cost. For this result to be conclusive, we need to perfom tests for large $n$.

\section{Conclusion}

With the examples and the programs discussed, we conclude that the tranformation of a non-straight line programs(with branching) in general increases the circuit complexity. The experiments on the implementation and the operations ........
\pagebreak

>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=7cm]{fsort3.pdf} 
\caption{Runtime for Insertion sort, nbit=4} 
\label{fig:image_sf3} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=7cm]{fsort4.pdf} 
\caption{Runtime for Insertion sort, nbit=6} 
\label{fig:image_sf4} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=7cm]{fsort5.pdf} 
\caption{Run time for Insertion sort, nbit=8} 
\label{fig:image_sf5} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!h]%on ouvre l'environnement figure
\centering
\includegraphics[width=7cm]{fsort6.pdf} 
\caption{CPU time for Insertion sort, nbit=4} 
\label{fig:image_sf6} %l'étiquette pour faire référence à cette image
\end{figure}

@@

\begin{figure}[!H]
\centering
\includegraphics[width=7cm]{fsort2.pdf} 
\caption{Runtime Comparison for insertion sort} 
\label{fig:image_sf2} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}[!H]%nouvre l'environnement figure
\centering
\includegraphics[width=7cm]{fsort1.pdf} 
\caption{Curve fitting for insertion sort}
\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
\end{figure}

@@

When we increase the security of the system by setting the parameters to  $(N = 256,\eta  = 16, \mu = 2, s_1 = 5000, s_2 = 5)$(as suggested in \cite{cryptoeprint:2009:571}) which ensures $25$ bits of security, the Odd-Even sorting algorithm on  $4$ sequences, each of $4$ bits takes hours. By lowering the security level to only $8$ bits using the parameters :$(N = 16, \eta = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which we believe is an implementation bug in the bootstrapping mechanism. Lowering the security even further to only $5$ bits using the parameters: $(N = 8, \eta = 2^8, \mu = 4, s_1 = 65, s_2 = 5)$, and testing odd-even sorting for $32$ sequences of $6$ bits each took more than an hour. However, increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \eta = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2}. The results show that this set of parameters provide a better security and at almost no extra cost. For this result to be conclusive, we need to perfom tests for large $n$. For our last test, we set the parameters to  $(N = 8, \eta = 2^{200}, \mu = 8, s_1 = 8, s_2 = 5)$ which gave us incorrect decryption. We note that decryption fails in case the depth is too small for recrypt to function.

\section{Conclusion}
With the examples and the programs discussed, we conclude that the tranformation of a non-straight line program on unencrypted data(with branching) into a straight line program on encrypted data increases the circuit complexity. We experimentally measured the cost of different operations on encrypted data. The existing implementation of Smart-Vercauteren scheme remains practical only for $1$ bit of security, when a user wants to apply a sorting algorithm on his encrypted bit sequences.
